Paper on the carbonate chemistry at Ny-Ålesund

### 2020-04-20 paper.Rmd
now a tsibble

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds"))) 
d <- d_all %>% 
  #dplyr::select
  #dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
  dplyr::mutate(year_month = format(datetime, '%Y-%m')) %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) #depth is a string
```

>>>>

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tsibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds")), index = datetime) 
d <- d_all %>% 
  #dplyr::select
  #dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
  dplyr::mutate(year_month = format(datetime, '%Y-%m')) %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) #depth is a string
```
